Report on the Third Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE3)

### 2015-10-25 WSSSPE3/report/wg_appendix_software_credit.tex
finished discussion of day 1 in SC appendix

The group also discussed separating quantitative measures (e.g., number of citations) from the value of a work in order to give credit, moving towards qualitative or anecdotal evidence of value.

PageRank for citations, based on number of mentions

market penetration or adoption rate in a community as a metric, although it was not clear how this would be measured.

Finally, the concept a software tool's uniqueness or indispensability to a community was mentioned, with value being characterized by a particular piece of software either offering unique capabilities or doing something better, faster, or with less computational requirements than other offerings.

>>>>

The group also discussed separating quantitative measures (e.g., number of citations) from the value of a work in order to give credit, moving towards qualitative or anecdotal evidence of value.
Other topics brought up included a form of PageRank~\cite{Brin1998} for citations, based on number of mentions, and using market penetration or adoption rate in a community as a metric, although it was not clear how this would be measured.
Finally, the concept a software tool's uniqueness or indispensability to a community was mentioned, with value being characterized by a particular piece of software either offering unique capabilities or doing something better, faster, or with less computational requirements than other offerings.

On the second day of WSSSPE3, the working group decided to put aside the taxonomy of contributions and focus on software citations to ensure developers receive credit (regardless of contribution).
Eventually, once standardizing software citations, the goal would be to return to establishing different roles\slash contributions for this credit.
